19Q1

### 2019-05-03 19Q1.Rmd
update Rmd

This comprehensive cancer cell line information was curated by both Daniel Charytonowicz and myself.
```{r dan_ccl_database}
ccl_converter <- read.delim("./data_munging/cell_line_database_v1_20180911.tsv", row.names = 1, sep = "\t", header = TRUE)
ccl_lineage_converter <- unique(ccl_converter[, c("Broad_ID", "grouped_general_doid", "group_general_lineage_name")])
lineage_converter <- unique(select(lineage_converter, grouped_general_doid, group_general_lineage_name))
ccl_histologies <- read.delim("./data_munging/ccl_histologies_metadata.csv", sep = ",", header = TRUE, row.names = 1)
```

@@

**RUN THIS IN TEH EVENING**
```{r, eval=FALSE}
ccle_hists <- unique(select(ccle_ptmuts, Broad_ID, Primary.Disease)) %>% count(Primary.Disease)
ccle_hists$Perc <- ccle_hists$n / sum(ccle_hists$n) * 100
ccle_hists$Dataset <- "CCLE"
ctrp_hists <- unique(select(ctrp_ptmuts, Broad_ID, Primary.Disease)) %>% count(Primary.Disease)
ctrp_hists$Perc <- ctrp_hists$n / sum(ctrp_hists$n) * 100
ctrp_hists$Dataset <- "CTRP"
gdsc_hists <- unique(select(gdsc_ptmuts, Broad_ID, Primary.Disease)) %>% count(Primary.Disease)
gdsc_hists$Perc <- gdsc_hists$n / sum(gdsc_hists$n) * 100
gdsc_hists$Dataset <- "GDSC"

drug_hists <- rbind(ccle_hists, ctrp_hists, gdsc_hists)
drug_hists$Primary.Disease <- as.character(drug_hists$Primary.Disease)

ggplot(drug_hists, aes(x = Dataset, y = n, fill = Primary.Disease)) +
  geom_bar(stat = "identity", color = "black")
```

@@

Kolmogorov-Smirnov tests comparing DGLs that are in a G2P DGL and not.
```{r drug_KS_tests, eval=TRUE, warning=FALSE, fig.height=6, fig.width=12}
# g2p_corr_all <- G2PCorrTable(ccle_ptmuts_df = ccle_ptmuts, ctrp_ptmuts_df = ctrp_ptmuts, gdsc_ptmuts_df = gdsc_ptmuts)
saveRDS(g2p_corr_all, "./data_munging/rds/g2p_corr_all.rds")
g2p_corr_all <- readRDS("./data_munging/rds/g2p_corr_all.rds")
g2p_mut_stats <- G2PCorrStatsTables(corr_df = g2p_corr_all, table_type = "mutation")

>>>>

This comprehensive cancer cell line information was curated by both Daniel Charytonowicz and myself.
```{r dan_ccl_database}
ccl_converter <- read.delim("./data_munging/cell_line_database_v1_20180911.tsv", row.names = 1, sep = "\t", header = TRUE)
ccl_lineage_converter <- unique(ccl_converter[, c("Broad_ID", "grouped_general_doid", "group_general_lineage_name")])
lineage_converter <- unique(select(ccl_lineage_converter, grouped_general_doid, group_general_lineage_name))
ccl_histologies <- read.delim("./data_munging/ccl_histologies_metadata.csv", sep = ",", header = TRUE, row.names = 1)
```

@@

## Histology distributions

```{r histology_dists_data, eval=FALSE}
ccle_hists <- unique(select(ccle_ptmuts, Broad_ID, Primary.Disease)) %>% count(Primary.Disease)
ccle_hists$Perc <- ccle_hists$n / sum(ccle_hists$n) * 100
ccle_hists$Dataset <- "CCLE"
ctrp_hists <- unique(select(ctrp_ptmuts, Broad_ID, Primary.Disease)) %>% count(Primary.Disease)
ctrp_hists$Perc <- ctrp_hists$n / sum(ctrp_hists$n) * 100
ctrp_hists$Dataset <- "CTRP"
gdsc_hists <- unique(select(gdsc_ptmuts, Broad_ID, Primary.Disease)) %>% count(Primary.Disease)
gdsc_hists$Perc <- gdsc_hists$n / sum(gdsc_hists$n) * 100
gdsc_hists$Dataset <- "GDSC"
crispr_hists <- unique(select(crispr_ptmuts, Broad_ID, Primary.Disease)) %>% count(Primary.Disease)
crispr_hists$Perc <- crispr_hists$n / sum(crispr_hists$n) * 100
crispr_hists$Dataset <- "CRISPR"

drug_hists <- rbind(ccle_hists, ctrp_hists, gdsc_hists, crispr_hists) %>% drop_na(Primary.Disease)
drug_hists$Dataset <- factor(drug_hists$Dataset, levels = c("CCLE", "CTRP", "GDSC", "CRISPR"))
drug_hists$Primary.Disease <- as.character(drug_hists$Primary.Disease)
drug_hists$Primary.Disease <- gsub(" cancer", "", drug_hists$Primary.Disease)
# saveRDS(drug_hists, "./data_munging/rds/histology_distributions.rds")
```

```{r histology_dists, fig.height=4.5, fig.width=4}
drug_hists <- readRDS("./data_munging/rds/histology_distributions.rds")
png(filename = "./plots/manuscript/histology_distributions.png", width = 8, height = 9, units = "in", res = 500)
ggplot(drug_hists, aes(x = Dataset, y = n, fill = Primary.Disease)) +
  geom_bar(stat = "identity", color = "black") +
  scale_y_continuous(breaks = seq(0, 850, by = 50), labels = seq(0, 850, by = 50)) +
  guides(fill = guide_legend(title = "Histology", ncol = 1)) +
  labs(y = "Count")
dev.off()
```

@@

Kolmogorov-Smirnov tests comparing DGLs that are in a G2P DGL and not.
```{r drug_KS_tests, eval=TRUE, warning=FALSE, fig.height=6, fig.width=12}
# g2p_corr_all <- G2PCorrTable(ccle_ptmuts_df = ccle_ptmuts, ctrp_ptmuts_df = ctrp_ptmuts, gdsc_ptmuts_df = gdsc_ptmuts)
# saveRDS(g2p_corr_all, "./data_munging/rds/g2p_corr_all.rds")
g2p_corr_all <- readRDS("./data_munging/rds/g2p_corr_all.rds")
g2p_mut_stats <- G2PCorrStatsTables(corr_df = g2p_corr_all, table_type = "mutation")
